Carbonate chemistry at Ny-Ålesund

### 2021-11-25 awipev-CO2.Rmd
testing despike on pHint_tot_sf

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")

@@

# bind new calibrated pH data to the seafet data set.
names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
d_all <- dplyr::bind_cols(d_all, seafet_calib )

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script

>>>>

if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)

@@

# bind new calibrated pH data to the seafet data set.
names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")

##########  Despike() ###########
d_all <- d_all %>%   
  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
  )

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* sal_mix_interp: interpolated salinity sal_mix. It is used to have as many spec pH to display (some are during missing data)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* temp_mix_interp: interpolated temperature temp_mix. It is used to have as many spec pH to display (some are during missing data)
* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script
